Reproducibility in plant pathology: where do we stand and a way forward

### 2022-04-25 analysis/paper/paper.Rmd
load packages necessary to knit the paper
specify the repository so that the paper knits in RStudio
add dplyr version to paper

install.packages(setdiff(packages, rownames(installed.packages())))

@@

Each journal was classified as to whether they were completely open (TRUE), behind a paywall (FALSE) or a combination (BOTH).
The five-year impact factor for 2022 for each journal was retrieved from InCites Journal Citation Reports, Clarivate Analytics and entered in a separate sheet in the Google sheets file.
This was downloaded, saved as an Open Document Spreadsheet (ODS) file and is left-joined with the article notes using a `left_join()` from the 'dplyr' package [@Wickham2020] for analysis when a custom function for this analysis, `import_notes()`, was executed.

>>>>

install.packages(setdiff(packages,
                         rownames(installed.packages())),
                 repos = "http://cran.us.r-project.org")

invisible(
  lapply(
    packages,
    library,
    character.only = TRUE
  )
)

@@

Each journal was classified as to whether they were completely open (TRUE), behind a paywall (FALSE) or a combination (BOTH).
The five-year impact factor for 2022 for each journal was retrieved from InCites Journal Citation Reports, Clarivate Analytics and entered in a separate sheet in the Google sheets file.
This was downloaded, saved as an Open Document Spreadsheet (ODS) file and is left-joined with the article notes using a `left_join()` from the 'dplyr' package (version `r packageVersion("dplyr")`) [@Wickham2020] for analysis when a custom function for this analysis, `import_notes()`, was executed.
